R Notebook

### 2019-05-29 ICS_Cleaning.Rmd
includes edits from mismatched donors and new excluded sample Nk2586

```{r write files to "clean" directory}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
df.list<-list(CD4_Counts.csv, CD4_Cytokine.csv, CD4_MFI.csv, CD4_Positive.csv,
              CD4.csv, CD8_Counts.csv, CD8_Cytokine.csv, GD_Counts.csv,
              GD_Cytokine.csv)
dfnames<-list("CD4_Counts", "CD4_Cytokine", "CD4_MFI", "CD4_Positive",
              "CD4", "CD8_Counts", "CD8_Cytokine", "GD_Counts",
              "GD_Cytokine")
newfilenames<-paste(dfnames, "clean", date(), ".csv", sep="_")
#write.csv(df.list[1], file= newfilenames[1])
write.csv(CD4_Counts.csv, file = "CD4_Counts_clean.csv")
write.csv(CD4_Cytokine.csv, file = "CD4_Cytokine_clean.csv")
write.csv(CD4_MFI.csv, file = "CD4_MFI_clean.csv")
write.csv(CD4_Positive.csv, file = "CD4_Positive_clean.csv")
write.csv(CD4.csv, file = "CD4_clean.csv")
write.csv(CD8_Counts.csv, file = "CD8_Counts_clean.csv")
write.csv(CD8_Cytokine.csv, file = "CD8_Cytokine_clean.csv")
write.csv(GD_Counts.csv, file = "GD_Counts_clean.csv")
write.csv(GD_Cytokine.csv, file = "GD_Cytokine_clean.csv")
write.csv(DonorInfo, file = "ICS_Donor_Info_clean.csv")
```

>>>>

```{r write files to "clean" directory}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
df.list<-list(CD4_Counts.csv, CD4_Cytokine.csv, CD4_MFI.csv, CD4_Positive.csv,
              CD4.csv, CD8_Counts.csv, CD8_Cytokine.csv, GD_Counts.csv,
              GD_Cytokine.csv)
dfnames<-list("CD4_Counts", "CD4_Cytokine", "CD4_MFI", "CD4_Positive",
              "CD4", "CD8_Counts", "CD8_Cytokine", "GD_Counts",
              "GD_Cytokine")
newfilenames<-paste(dfnames, "clean", date(), ".csv", sep="_")
#write.csv(df.list[1], file= newfilenames[1])
write.csv(CD4_Counts.csv, file = "ICS_CD4_Counts_clean.csv")
write.csv(CD4_Cytokine.csv, file = "ICS_CD4_Cytokine_clean.csv")
write.csv(CD4_MFI.csv, file = "ICS_CD4_MFI_clean.csv")
write.csv(CD4_Positive.csv, file = "ICS_CD4_Positive_clean.csv")
write.csv(CD4.csv, file = "ICS_CD4_clean.csv")
write.csv(CD8_Counts.csv, file = "ICS_CD8_Counts_clean.csv")
write.csv(CD8_Cytokine.csv, file = "ICS_CD8_Cytokine_clean.csv")
write.csv(GD_Counts.csv, file = "ICS_GD_Counts_clean.csv")
write.csv(GD_Cytokine.csv, file = "ICS_GD_Cytokine_clean.csv")
write.csv(DonorInfo, file = "ICS_Donor_Info_clean.csv")
```
